### 2021-11-24 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@11853fb2c1163b5fc2860dcbc4ed015897b46ca5 🚀

This chapter uses simulation models to investigate the relationship
between species relative abundance, sampling effort, and probability of
observing an interaction between species in order to aid in the design
of samples of ecological interactions, and to provide a null expectation
of false-negative probability for a dataset of a given size. Further it
then proposes a method for optimizing the spatial sampling locations to
maximize the probability of detecting an interaction between two species
given a fixed number of total of observations, and the distributions of
each species. This addresses the optimization of monitoring network part
of the flow from data to mitigation at the top of fig.~\ref{fig:thesis},
left. As explored in the previous chapter, there are false-negatives in
interaction data. However, there is more than one way to observe a
false-negative when sampling interactions. fig.~\ref{fig:fnrtaxonomy}
shows a taxonomy of false-negatives in occurrence, co-occurrence, and
interaction data.

@@

The first result is to compute a null expectation of the probability of
an interaction false-negative as a function number of total observations
of individuals of \emph{any species}. This is done by simulating the
process of observation, where the probability of observing a given
species is its relative abundance. We use a log-normal distribution of
relative abundance (Hubbell 2001) and simulating the process of
observation on food-webs generated using the niche model (Williams \&
Martinez 2000) with connectance parameterized by the flexible-links
model (MacDonald \emph{et al.} 2020). An example of this relation for
networks with varying spceies richness is shown in fig.~\ref{fig:fnr}.

@@

\begin{figure}
\centering
\includegraphics{./figures/ch1.png}
\caption{Chapter One conceptual figure. Left: the sources of data and
how they can be synthesized. Right: The flow from data to interaction
prediction using a few different interaction prediction models.}
\end{figure}

@@

Here we show the in-progress results, which are the prerequisites for
the analysis outlined above: phylogenies for both plant and bee species
(fig.~\ref{fig:phylo}) and species distribution models for all species
(an example shown in fig.~\ref{fig:example_sdm}).

@@

At the moment, we have derived phylogenies (fig.~\ref{fig:phylo}) and
SDMs (fig.~\ref{fig:example_sdm}) for all the species present in the
Colorado GBIF metaweb. I've also been exploring the data available from
Julian Resasco. The primary constraint on further progress is that we
are waiting on the finalization of a data sharing agreement with RMBL.

@@

\begin{figure}
\hypertarget{fig:ch3}{%
\centering
\includegraphics{./figures/ch3.png}
\caption{foo}\label{fig:ch3}
}
\end{figure}

@@

\textbf{TK} The biggest challenge in implementing simulated annealing in
this context is defining a proposal function for landscape
modifications. At the moment this is done by computing the
minimum-spanning-tree (MST) of the spatial nodes, and then proposing
corridors that connect nodes that are already connected in the MST.

\textbf{TK} The goal to rank the cells in the raster by priority based
on how many times they are converted in the distribution of ``good''
corridors after simulated annealing has reached a pseudoequilibrium.
Further, the final component of this chapter is measuring the effect of
land-use change on the robustness of the optimized corridor. By
simulating various neutral models of urban and agricultural sprawl, we
can determine if the proposed modifications

@@

\begin{quote}
Describing expected/anticipated contributions of the thesis. Very
important for QE. This should be at least half a page.
\end{quote}

@@

By using the success of numerical-weather prediction and the Earth
monitoring system that supports it as a model,

>>>>

This chapter uses simulation models to investigate the relationship
between species relative abundance, sampling effort, and probability of
observing an interaction between species in order to aid in the design
of samples of ecological interactions, and to provide a null expectation
of false-negative probability for a dataset of a given size. Further it
then proposes a method for optimizing the spatial sampling locations to
maximize the probability of detecting an interaction between two species
given a fixed number of total of observations and the distributions of
each species. This addresses the optimization of monitoring network part
of the flow from data to mitigation at the top of fig.~\ref{fig:thesis},
left. There is more than one way to observe a false-negative when
sampling interactions. fig.~\ref{fig:fnrtaxonomy} shows a taxonomy of
false-negatives in occurrence, co-occurrence, and interaction data. This
chapter untangles the relationship between co-occurrence false-negatives
and interaction false-negatives.

@@

We begin by proposing a method to compute a null expectation of the
probability of an interaction false-negative as a function number of
total observations of individuals of \emph{all species in the species
pool}. This is done by simulating the process of observation, where the
probability of observing a given species is its relative abundance. We
use a log-normal distribution of relative abundance (Hubbell 2001) and
simulating the process of observation on food-webs generated using the
niche model (Williams \& Martinez 2000) with connectance parameterized
by the flexible-links model (MacDonald \emph{et al.} 2020). An example
of this relation for networks with varying spceies richness is shown in
fig.~\ref{fig:fnr}.

@@

\begin{figure}
\centering
\includegraphics{./figures/ch1.png}
\caption{Chapter One conceptual figure. Left: the sources of data and
how they can be combined. Right: The flow from data to interaction
prediction using a few different interaction prediction models.}
\end{figure}

@@

The in-progress results are the prerequisites for the analysis outlined
above: phylogenies for both plant and bee species (appendix figure one)
and species distribution models for all species (an example shown in
appendix figure two).

@@

At the moment, we have derived phylogenies and SDMs for all the species
present in the Colorado GBIF metaweb (appendix figures one and two).
I've also been exploring the data available from Julian Resasco. The
primary constraint on further progress is that we are waiting on the
finalization of a data sharing agreement with RMBL.

@@

\begin{figure}
\hypertarget{fig:ch3}{%
\centering
\includegraphics{./figures/ch3.png}
\caption{A conceptual example of how we go from a map of landcover with
a set of points where occurrence of a species has been recorded (top
left), to the set of all possible landscape modifications (green box,
where each point in the green box is a unique landscape modification,
with three examples shown as pink, red and orange dots), to computing
resistance surfaces based on proposed landscape modifications (center)
and then simulate the distribution of extinction times for a
metapopulation in this new landscape (right).}\label{fig:ch3}
}
\end{figure}

@@

The biggest challenge in implementing simulated annealing in this
context is defining a proposal function for landscape modifications. At
the moment this is done by computing the minimum-spanning-tree (MST) of
the spatial nodes, and then proposing corridors that connect nodes that
are already connected in the MST. The primary reason for doing this is
the cut down the size of the solution space to enable quicker
convergence, although the final software that implements this algorithm
will enable alternative methods of proposing modifications.

The goal output of this chapter is not only to provide a set of discrete
corridor options, but also to rank the cells in the raster by priority
based on how many times they are converted in the distribution of
``good'' corridors after simulated annealing has reached a
pseudoequilibrium. Further, the final component of this chapter is
measuring the effect of land-use change on the robustness of the
optimized corridor by simulating various neutral models of urban and
agricultural sprawl, and determining if the proposed modifications still
maximize time-until-extinction when the landcover in the landscape is
not static.

@@

@@

\textbf{TK} By using the success of numerical-weather prediction and the
Earth monitoring system that supports it as a model,
